### 2025-05-21 sec/authoring-workflow.tex
[update] added system-prompt
[update] box for system prompt and minor improvements to the table
[update] fix newline in system prompt

>>>>

\subsection{System Prompt}
\label{subsec:system-prompt}
Fig. \ref{fig:system-prompt} shows the system prompt defined for the Authoring Assistant.

\begin{figure}[h]
    \centering
    \begin{tcolorbox}[colback=gray!10, colframe=gray!50, boxrule=0.5pt, arc=2pt,
        left=6pt, right=6pt, top=4pt, bottom=4pt]
        \VerbatimInput[fontsize=\small, formatcom=\normalfont]{system-prompt/system-prompt.txt}
    \end{tcolorbox}
    \vspace{-0.5em}
    \caption{System-Prompt defined for the Authoring Assistant}
    \label{fig:system-prompt}
\end{figure}
